Eddy covariance towers as sentinels of abnormal radioactive material releases

### 2024-09-12 manuscript/manuscript.tex
espr submission re-edits

\author{
	\href{https://orcid.org/0000-0002-5924-2464}{\includegraphics[scale=0.06]{orcid.pdf}\hspace{1mm}Jemma Stachelek$^1$} \\
	$^1$ High Performance Computing Division\\
	Los Alamos National Laboratory\\
	Los Alamos, NM, USA, 87544 \\
	\texttt{jsta@lanl.gov} \\
	\And
	Vachel A. Kraklow$^2$ \\
	$^2$ Earth and Environmental Sciences Division\\
	Los Alamos National Laboratory\\
	Los Alamos, NM, USA, 87544 \\
	\And
	E. Christi Thompson$^3$ \\
	$^3$ Computer, Computational, and Statistical Sciences Division\\
	Los Alamos National Laboratory\\
	Los Alamos, NM, USA, 87544 \\
	\And
	\textbf{L. Turin Dickman}$^2$ \\
	$^2$ Earth and Environmental Sciences Division\\
	Los Alamos National Laboratory\\
	Los Alamos, NM, USA, 87544 \\
	\And
	\textbf{Emily Casleton}$^3$ \\
	$^3$ Computer, Computational, and Statistical Sciences Division\\
	Los Alamos National Laboratory\\
	Los Alamos, NM, USA, 87544 \\
	\And
	\textbf{Sanna Sevanto}$^2$ \\
	$^2$ Earth and Environmental Sciences Division\\
	Los Alamos National Laboratory\\
	Los Alamos, NM, USA, 87544 \\
	\And
	\textbf{Ann Junghans}$^4$ \\
	$^4$ Nuclear and Engineering Nonproliferation Division\\
	Los Alamos National Laboratory\\
	Los Alamos, NM, USA, 87544
}

@@

>>>>

\author{
	\href{https://orcid.org/0000-0002-5924-2464}{\includegraphics[scale=0.06]{orcid.pdf}\hspace{1mm}Corresponding Author: Jemma Stachelek$^1$} \\
	$^1$ High Performance Computing Division\\
	Los Alamos National Laboratory\\
	Los Alamos, NM, USA, 87544 \\
	\texttt{jsta@lanl.gov} \\
	\And
	Vachel A. Kraklow$^2$ \\
	$^2$ Earth and Environmental Sciences Division\\
	Los Alamos National Laboratory\\
	Los Alamos, NM, USA, 87544 \\
	\And
	E. Christi Thompson$^3$ \\
	$^3$ Computer, Computational, and Statistical Sciences Division\\
	Los Alamos National Laboratory\\
	Los Alamos, NM, USA, 87544 \\
	\And
	\textbf{L. Turin Dickman}$^2$ \\
	$^2$ Earth and Environmental Sciences Division\\
	Los Alamos National Laboratory\\
	Los Alamos, NM, USA, 87544 \\
	\And
	\textbf{Emily Casleton}$^3$ \\
	$^3$ Computer, Computational, and Statistical Sciences Division\\
	Los Alamos National Laboratory\\
	Los Alamos, NM, USA, 87544 \\
	\And
	\textbf{Sanna Sevanto}$^2$ \\
	$^2$ Earth and Environmental Sciences Division\\
	Los Alamos National Laboratory\\
	Los Alamos, NM, USA, 87544 \\
	\And
	\textbf{Ann Junghans}$^4$ \\
	$^4$ Nuclear and Engineering Nonproliferation Division\\
	Los Alamos National Laboratory\\
	Los Alamos, NM, USA, 87544
}

@@

\subsection*{Ethical Approval}

Not applicable

\subsection*{Consent to Participate}

Not applicable

\subsection*{Consent to Publish}

Not applicable

\subsection*{Availability of Data and Materials}

No new data was produced in this study. All data used is available publicly from their respective sources and archived permanently with digital object identifiers.
